Nice people or potential cooperators when keeping promises

### 2019-08-14 behavioral-promises/behavioral-promises.tex
Relax margin
.

@@

\institute{
        Said Jiménez \at
     Department of Psychology, National University of México (UNAM) \\
     \email{\href{mailto:said.ejp@gmail.com}{\nolinkurl{said.ejp@gmail.com}}}  %  \\
%             \emph{Present address:} of F. Author  %  if needed
    \and
        Eduardo A. Garza-Villarreal \at
     Institute of Neurobiology, UNAM \\
     \email{\href{mailto:egarza@gmail.com}{\nolinkurl{egarza@gmail.com}}}  %  \\
%             \emph{Present address:} of F. Author  %  if needed

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Social closeness will reduce the decision of breaking the promise.
  According to the instrumental motivation, we expect that subjects keep
  their promises with friends for the purpose of facilitating future
  cooperation, which probably can be extended even beyond the trials in
  the experiment. We also expect, although to a lesser extent, that the
  subjects keep promises to strangers, with the purpose of facilitating
  cooperation during the experiment. Finally, we anticipate that the
  participants break the promises to the computer because it is a
  partner without any social closeness and they could not ensure
  cooperation in future trials. It should be noted that if the
  participants keep the promises to the computer, evidence would be
  given in favor of intrinsic motivation.
\end{enumerate}

@@

All models presented below were programmed in R via the \textbf{brms}
package (Bürkner 2017; R Core Team 2019), which performs the inference
using sampling by Markov chain Monte Carlo through \textbf{Stan} (Stan
Development Team 2018). For each model, the posteriors distributions of
all parameters were approximated with four chains of 2000 iterations
each, the first 1000 iterations of each chain were discarded (burning
period), for a total of 4000 post burning samples. Models convergence
was evaluated through visual inspection of the chains and calculation of
the \(\hat{R}\) statistic, which for all parameters was 1, that can be
interpreted as convergence. Vaguely informative prior distributions were
used for the parameters of interest in the models, which allows the data
to dominate the inference, also assumes as little as possible regarding
the nature of the phenomenon, which could be adequate for the current
state of evidence in the problem we are studying (McElreath 2018).

>>>>

\AtBeginDocument{%
  \paperwidth=\dimexpr
    1in + \oddsidemargin
    + \textwidth
    % + \marginparsep + \marginparwidth
    + 1in + \oddsidemargin
  \relax
  \paperheight=\dimexpr
    1in + \topmargin
    + \headheight + \headsep
    + \textheight
    % + \footskip
    + 1in + \topmargin
  \relax
  \usepackage[pass]{geometry}\relax
}

@@

\institute{
        Said Jiménez \at
     Department of Psychology, National University of México (UNAM) \\
     \email{\href{mailto:said.ejp@gmail.com}{\nolinkurl{said.ejp@gmail.com}}}  %  \\
%             \emph{Present address:} of F. Author  %  if needed
    \and
        Eduardo A. Garza-Villarreal \at
     Institute of Neurobiology, UNAM \\
     \email{\href{mailto:egarza@gmail.com}{\nolinkurl{egarza@gmail.com}}}  %  \\
    }

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Social closeness will reduce the decision of breaking the promise.
  According to the instrumental motivation, we expect that subjects keep
  their promises with friends for the purpose of facilitating future
  cooperation, which probably can be extended even beyond the trials in
  the experiment. We also expect, although to a lesser extent, that the
  subjects keep promises to strangers, with the purpose of facilitating
  cooperation during the experiment. Finally, we anticipate that the
  participants break the promises to the computer because it is a
  partner without any social closeness and they could not ensure
  cooperation in future trials. It should be noted that if the
  participants keep the promises to the computer, evidence would be
  given in favor of intrinsic motivation (Pre-registered hypothesis is available
here: \url{https://osf.io/53jqr}).
\end{enumerate}

@@

All models presented below were programmed in R via the \textbf{brms}
package (Bürkner 2017; R Core Team 2019), which performs the inference
using sampling by Markov chain Monte Carlo through \textbf{Stan} (Stan
Development Team 2018). For each model, the posteriors distributions of
all parameters were approximated with four chains of 2000 iterations
each, the first 1000 iterations of each chain were discarded (burning
period), for a total of 4000 post burning samples. Models convergence
was evaluated through visual inspection of the chains and calculation of
the \(\hat{R}\) statistic, which for all parameters was 1, that can be
interpreted as convergence (All data and R scripts are available at 
\url{https://github.com/saidejp/motivations-promises}. Vaguely informative 
prior distributions were used for the parameters of interest in 
the models, which allows the data to dominate the inference, also assumes as
little as possible regarding the nature of the phenomenon, which could be 
adequate for the current state of evidence in the problem 
we are studying (McElreath 2018).
